---
title: "Lab 3 Team All Stars"
author: "Johnny Tamanaha, Emily Archambault, Eugene Miller, Kaiyuan Fan, Jingzhi Zhang"
date: "9/13/2019"
output: html_document
---
```{r, setup, echo = FALSE, message = FALSE}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```


---

__Question: Does smoking affect health?__

---

__Why is this question important?__

---

__Team Plot:__

---

__Conclusion:__

---

__Recommendation for Action:__

---

__Individual Sections:__

### Eugene Miller
```{r Eugenes_Code, echo = FALSE, message = FALSE}
health.labs <- c("Excellent Health", "Very Good Health", "Good Health", "Fair Health", "Poor Health")
names(health.labs) <- c("excellent", "very good", "good", "fair", "poor")
smoke.labs <- c("Nonsmoker", "Smoker")
names(smoke.labs) <- c("0", "1")

ggplot(data = cdc, mapping = aes(x = weight, y = height)) +
  geom_jitter() +
  geom_smooth(mapping = aes(color = genhlth), se = FALSE) +
  labs(title = "A Comparison of Height Versus Weight in Smokers and Nonsmokers Across Health Status", y = "Height", x = "Weight") +
  guides(color = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 12)) +
  facet_wrap(genhlth~smoke100, labeller = labeller(smoke100 = smoke.labs, genhlth = health.labs))
```

__Explanation of Findings:__
There are no major differences between smokers and nonsmokers in terms of height versus weight corrolations even when accounting for health status. This suggestes that health status plays a larger role in determening the ratio of one's height versus weight rather than whether or not an individual is a smoker. This would seem to make sense, as whether or not an individual smokes may not be the largest factor impacting their health. For example, a nonsmoker with a serious illness is likely to not have the same weight to height ratio as a smoker who otherwise is in perfect health. 

---

