---
title: "Lab 3 Team All Stars"
author: "Johnny Tamanaha, Emily Archambault, Eugene Miller, Kaiyuan Fan, Jingzhi Zhang"
date: "9/13/2019"
output: html_document
---
```{r, setup, echo = FALSE, message = FALSE, error=TRUE, warning=FALSE}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```


---

## Question: Does smoking affect health?

---

## Why is this question important?

---

## Team Plot:

---

__Team Plot:__
```{r, echo=FALSE}
ggplot(cdc) +
  geom_bar(mapping=aes(x=genhlth, fill=smoke100==1), position="dodge") +
  labs(x="General Health", y="# of People", fill="Did You Smoke 100 Cigarettes?", title="Proportions of Subjects Who've Smoked 100 Cigarettes per Each General Health Category")
```
=======
## Conclusion:

---

## Recommendation for Action:

---

## Individual Sections:

### Eugene Miller
```{r Eugenes_Code, echo = FALSE, message = FALSE}
health.labs <- c("Excellent Health", "Very Good Health", "Good Health", "Fair Health", "Poor Health")
names(health.labs) <- c("excellent", "very good", "good", "fair", "poor")
smoke.labs <- c("Nonsmoker", "Smoker")
names(smoke.labs) <- c("0", "1")

ggplot(data = cdc, mapping = aes(x = weight, y = height)) +
  geom_jitter() +
  geom_smooth(mapping = aes(color = genhlth), se = FALSE) +
  labs(title = "A Comparison of Height Versus Weight in Smokers and Nonsmokers Across Health Status", y = "Height", x = "Weight") +
  guides(color = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 11.5)) +
  facet_wrap(genhlth~smoke100, labeller = labeller(smoke100 = smoke.labs, genhlth = health.labs))
```

__Explanation of Findings:__
There are no major differences between smokers and nonsmokers in terms of height versus weight corrolations even when accounting for health status. This suggestes that health status plays a larger role in determening the ratio of one's height versus weight rather than whether or not an individual is a smoker. This would seem to make sense, as whether or not an individual smokes may not be the largest factor impacting their health. For example, a nonsmoker with a serious illness is likely to not have the same weight to height ratio as a smoker who otherwise is in perfect health. 

---

### Johnny Tamanaha
```{r, echo=FALSE, messgae=FALSE, error=TRUE}
smoke.labs <- c("Nonsmoker", "Smoker")
names(smoke.labs) <- c("0", "1")
ggplot(cdc) +
  geom_freqpoly(mapping=aes(x=age, color=genhlth), alpha=.6, bins=30) +
  facet_wrap(~smoke100, labeller = labeller(smoke100 = smoke.labs)) +
  labs(x="Age", y="Density", color="General Health", title="General Health Density vs Age Split by Smoker/NonSmoker")
```

**Findings**: Smokers seem more likely to have poor health at a older age while non-smokers seem to be more likely to have excellent/very good health at a younger age. Density vs Age Split by Smoker/NonSmoker.

---

### Kaiyuan Fan 
```{r, echo=FALSE, messgae=FALSE, error=TRUE}
ggplot(cdc, aes(x = smoke100))+
 geom_bar(aes(fill = smoke100 == 1),alpha = 3/5, position = "identity", show.legend = TRUE) +
 labs(x= "smoke100", y="count", fill = "has smoked 100 cigarettes", title = "Count number of people smoke 100 cigarettes or more")
```
  __Explanation: My plot is to count the number of people who  smokes and who does smoke.
   If people smoke 100 cigarettes or more through life, then the smoke100 equals 1, which is green color on the plot. And if people doesn't smoke or smoke less than 100 cigarettes, the smoke100 equals 0, which is red showing on the plot. I find people who does not smoke are more than people smoke.


---