---
title: "Lab 3 Team All Stars"
author: "Johnny Tamanaha, Emily Archambault, Eugene Miller, Kaiyuan Fan, Jingzhi Zhang"
date: "9/13/2019"
output: html_document
---
```{r, setup, echo = FALSE, message = FALSE}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```


---

## Question: Does smoking affect health?

---

## Why is this question important?

---

## Team Plot:

---

<<<<<<< HEAD
__Team Plot:__
```{r}
ggplot(cdc) +
  geom_bar(mapping=aes(x=genhlth, fill=smoke100==1), position="dodge") +
  labs(x="General Health", y="# of People", fill="Did You Smoke 100 Cigarettes?", title="Proportions of Subjects Who've Smoked 100 Cigarettes per Each General Health Category")
```
=======
## Conclusion:

>>>>>>> master
---

## Recommendation for Action:

---

## Individual Sections:

### Eugene Miller
```{r Eugenes_Code, echo = FALSE, message = FALSE}
health.labs <- c("Excellent Health", "Very Good Health", "Good Health", "Fair Health", "Poor Health")
names(health.labs) <- c("excellent", "very good", "good", "fair", "poor")
smoke.labs <- c("Nonsmoker", "Smoker")
names(smoke.labs) <- c("0", "1")

ggplot(data = cdc, mapping = aes(x = weight, y = height)) +
  geom_jitter() +
  geom_smooth(mapping = aes(color = genhlth), se = FALSE) +
  labs(title = "A Comparison of Height Versus Weight in Smokers and Nonsmokers Across Health Status", y = "Height", x = "Weight") +
  guides(color = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 11.5)) +
  facet_wrap(genhlth~smoke100, labeller = labeller(smoke100 = smoke.labs, genhlth = health.labs))
```

__Explanation of Findings:__
There are no major differences between smokers and nonsmokers in terms of height versus weight corrolations even when accounting for health status. This suggestes that health status plays a larger role in determening the ratio of one's height versus weight rather than whether or not an individual is a smoker. This would seem to make sense, as whether or not an individual smokes may not be the largest factor impacting their health. For example, a nonsmoker with a serious illness is likely to not have the same weight to height ratio as a smoker who otherwise is in perfect health. 

---

__Individual Plots__

```{r}
smoke.labs <- c("Nonsmoker", "Smoker")
names(smoke.labs) <- c("0", "1")
ggplot(cdc) +
  geom_freqpoly(mapping=aes(x=age, color=genhlth)) +
  facet_wrap(~smoke100, labeller = labeller(smoke100 = smoke.labs)) +
  labs(x="Age", y="Density", color="General Health", title="General Health Density vs Age Split by Smoker/NonSmoker")
```

Findings: Smokers seem more likely to have poor health at a older age while non-smokers seem to be more likely to have excellent/very good health at a younger age. Density vs Age Split by Smoker/NonSmoker.

